### 2022-07-03 chapters/benchmarking/draft.tex
add : soa

\section{Introduction}
Since the objective of this thesis is to study various alternatives for reducing the energy consumption of software programs, this chapter will focus on this topic. We shall conduct extensive empirical research. This chapter describes the instruments required to conduct a successful experiment to measure the energy consumption of software applications.
In addition, the majority of the time we will conduct an analytical comparison; therefore, the goal is to develop a framework to assist practitioners in comparing various solutions in terms of energy consumption.

@@

We propose making certain enhancements to the benchmarking framework that was suggested by the collaboratory on Experimental Evaluation of Software \footnote{\url{http://evaluate.inf.usi.ch/}}. and Systems in Computer Science in order to address those problems.
Instead of only presenting the four primary aspects of their guidelines, which are \emph{measurement contexts} that indicate the software and hardware components that will alter or remain constant during the experiment. \emph{workloads} which identify the benchmarks to use in the experiment, as well as their inputs; \emph{metrics} that specify the attributes to be measured and how to assess them. \emph{Data analysis} show how to examine data and evaluate the outcomes of the analysis to offer insight into the assertions that arise from the study.

>>>>

\section{Introduction}
Because the goal of this thesis is to investigate various possibilities for improving the energy consumption of software programs, this chapter will be focusing on how to conduct effective experiments when comparing the energy consumption of softwares.
We will carry out substantial empirical investigation. This chapter discusses the tools needed to do a successful experiment measuring the energy consumption of software programs.
In addition, the majority of the time we will conduct an analytical comparison; therefore, the goal is to develop a framework to assist practitioners in comparing various solutions in terms of energy consumption.

@@

We propose making certain enhancements to the benchmarking framework that was suggested by the collaboratory on Experimental Evaluation of Software \footnote{\url{http://evaluate.inf.usi.ch/}}. and Systems in Computer Science in order to address those problems.
Instead of only presenting the four primary aspects of their guidelines, which are

### 2022-07-03 chapters/literature/draft_citations.tex
fix : bug where i cant add references
add : soa

% as for computer sience. In their paper~\cite{buytaert_statistically_nodate}, the authors  separated the start-up measurement from the steady state when comparing different Java optimizations.

\begin{figure}[!hbt]
    \center{\includegraphics[scale=0.3]{imgs/componentsofanexperiment}}
    \caption{The proposed decomposition of an experement\footnote{\url{http://evaluate.inf.usi.ch/}}}\label{fig:soa_expermiment component}
\end{figure}

>>>>

% as for computer sience. In their paper~\cite{buytaert_statistically_nodate}, the authors  separated the start-up measurement from the steady state when comparing different Java optimizations.
Another work, to make unify the bemchmarking methodology across different research works in the field of computer science, we can cite the paper~\cite{stephen_evaluate_2012}. In their approach they  divided any emprical experiment into four  components:

\begin{enumerate}
    \item \emph{measurement contexts} that indicate the software and hardware components that will alter or remain constant during the experiment.
    \item \emph{workloads} which identify the benchmarks to use in the experiment, as well as their inputs; 
    \item \emph{metrics} that specify the attributes to be measured and how to assess them. 
    \item \emph{Data analysis} show how to examine data and evaluate the outcomes of the analysis to offer insight into the assertions that arise from the study.
\end{enumerate}

Figure \ref{fig:soa_experiment_component} shows the four component presented in the article~~\cite{stephen_evaluate_2012}

\begin{figure}[!hbt]
    \center{\includegraphics[scale=0.3]{imgs/componentsofanexperiment}}
    \caption{The proposed decomposition of an experement~\cite{stephen_evaluate_2012}}\label{fig:soa_expermiment_component}
\end{figure}
